Missing the Point$\colon$ Non-Convergence in Multiple Imputation Procedures

### 2020-03-30 3.Thesis/1.SimulationStudy/Writeup/manuscript.Rmd
Use rticles package instead of resolving issues in csl myself.

---
title: "Missing the Point: Convergence of Multiple Imputation by Chained Equations Algorithms"
author: "Hanne I. Oberman"
date: "16-3-2020"
output: 
  pdf_document:
    keep_tex: true
    number_sections: true
bibliography: thesis.bib
documentclass: sagej
classoption: Royal, times, sageapa
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

@@

Feedback:

- Add more info about figure legends and axes.

@@

```{r}
# plot results
load("../Results/results.Rdata")

@@

# References

>>>>

---
title: Missing the Point$\colon$ Non-Convergence in Multiple Imputation Procedures
runninghead: Oberman
author:
- name: H. I. Oberman
  num: 1
address:
- num: 1
  org: Department of Methodology and Statistics, Utrecht University, Utrecht, The Netherlands
corrauth: "Hanne Oberman, Sjoerd Groenman building, Utrecht Science Park, Utrecht, The Netherlands."
email: h.i.oberman@uu.nl
abstract: "Lorem ipsum dolor sit amet, consectetur adipiscing elit. Aenean ut elit odio. Donec fermentum tellus neque, vitae fringilla orci pretium vitae. Fusce maximus finibus facilisis. Donec ut ullamcorper turpis. Donec ut porta ipsum. Nullam cursus mauris a sapien ornare pulvinar. Aenean malesuada molestie erat quis mattis. Praesent scelerisque posuere faucibus. Praesent nunc nulla, ullamcorper ut ullamcorper sed, molestie ut est. Donec consequat libero nisi, non semper velit vulputate et. Quisque eleifend tincidunt ligula, bibendum finibus massa cursus eget."
keywords: MICE; convergence; 
classoption:
  - Royal
  - times
bibliography: thesis.bib
bibliographystyle: sageh
output:
  rticles::sage_article:
    keep_tex: yes
---

```{r setup, include=FALSE}
#knitr::opts_chunk$set(echo = TRUE)
load("../Results/results.Rdata")
source("../2.CreateFigures.R")

@@

**Add more info about figure legends and axes.**

@@

```{r, fig.cap="Convergence diagnostics (means)"}
bias_means_plot + R_means_plot + AC_means_plot + plot_layout(nrow = 3, guides = "collect")
```

```{r, fig.cap="Convergence diagnostics (variances)"}
bias_sds_plot + R_sds_plot + AC_sds_plot + plot_layout(nrow = 3, guides = "collect")
```

```{r, fig.cap="Convergence diagnostics (regression coefficients)"}
bias_ests_plot + bias_R_sq_plot + cov_plot + plot_layout(nrow = 3, guides = "collect")
```

@@

<!-- # References -->
